Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-23 paper/paper.tex
Fix issue with text overflow
FINAL PAPEEER

In this research paper, we present and discuss our findings after running a quantitative data analysis 
on over 300,000 tickets taken from more than 38 open source projects. To this aim, we implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

@@

Another research paper that strenghtens the argument that readability is a quality 
factor in software tickets is the one presented by Hooimeijer et al. \cite{hooimeijer2007modeling}.
They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
investigating readability, daily load, submitter reputation, the whole changelog histories 
and severity. They conclude that not only readability in the textual fields of a ticket
influences the \emph{Time-To-Close}, but also that the presence of attachments and 
the number of comments have a clear lowering effect on the duration of triaging. On the 
other hand, the patch count and other similar fields did not provide significant 
value to the quality of tickets.

@@

The first information to be filled in by end users or developers on any issue tracking system
is the summary field, which holds a small description, usually between 5 and 30 words, of 
the request or bug being reported. In the study conducted by Rastkar et al. \cite{rastkar2010summarizing}, 
the authors investigated whether tickets could be summarized automatically and efficiently. What 
that implies is that developers would no longer be required to look at tickets on the whole, comprising of 
a large number of fields, but rather at a simple summary of a couple of lines 
encapsulating the whole information. The authors selected the Mozilla, Eclipse, GNOME and KDE 
open source projects and they asked volunteering university students to annotate 
the tickets in the issue tracking systems. More specifically, they wrote a summary 
of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
In parallel, Machine Learning algorithms were also employed to parse these summaries and 
learn how to efficiently create automated summaries for new bug reports. After both methods had been run, 
software developers were asked to rate these auto-generated summaries against the original ones; 
the conclusion was that existing conversation-based extractive summary generators used 
for software tickets produce the best results.

The work of Just et al. \cite{just2008towards} examines a rather different aspect
of quality in tickets - they are investigating the quality of the underlying issue 
tracking systems instead. 
After running a survey on 175 developers from Eclipse, Apache and Mozilla,
the authors applied a card sort in order to organize the comments into hierarchies to 
identify common patterns. Their findings can be summarized in the following top seven
suggestions: create differentiation between bug report difficulty levels between 
novices and experiences reporters, encourage users to input as much information as possible, 
add ability to merge tickets when needed, recognise and reward valuable bug reporters, integrate 
reputation into user profiles to mark experienced reporters and ensure the ability to expressively search through tickets.

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et al. \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
The conclusions they drew from running the evaluation process were rather 
interesting: terms such as segfault, deadlock, crash, hand or memory typically indicate
a severe bug, when analyzing the textual description they found that using simple
one line summaries resulted in less false positives and increased precision
levels, the classifier needs a large number of tickets in order to predict correctly, 
depending on how well a software project is modularised and, lastly, one can 
use a predictor per module rather than a universal one.

@@

\section{Building the Data Set}\label{building}
The first step towards building the data set was to create a tool that was able to execute all the necessary commands:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in mind, thus making it easy for others who might join the project to read 
    and understand the codebase; this would prove useful for developing the tool further;
    \item it is a compiled, statically typed language that produces cross-platform executables when building the application;
    this is helpful for our research as we can use any machine or cluster of computers regardless of the operating system 
    running on them and collect even larger number of tickets than what we have collected so far;
    \item it is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
    in our case, it helps by allowing access to goroutines, very lightweight threads that can scale even up to 
    millions; we use this powerful concept while fetching tickets from Jira or storing in the database - at one point, there were 
    more than 30,000 goroutines running at the same time.
  \end{itemize}

@@

This is the first command implemented in our tool - it is desgined to fetch, from any valid Jira URL, any number of tickets 
and then store everything inside an instance of BoltDB \cite{bolt}, a key-value pair 
database. The whole process is parallelized with the possibility of scaling even up to hundreds of goroutines
(i.e. lightweight threads) running concurrently.

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. The next step is to filter out the tickets based on the following criteria:
\begin{itemize}
  \item tickets are \emph{High Priority} - the ticket status marked as either Blocker, Critical, Major or High;
  \item tickets are closed with a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
  higher bound as well in order to eliminate outliers retrieved by Jira);
  \item remove outliers for all categories - some fields had extreme values for a small number of tickets (e.g. one ticket
  had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
  produced correct results (they were removed as they were skewing the results due to erroneous completion of fields).
\end{itemize}

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence \emph{Time-To-Close} and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence \emph{Time-To-Close} the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the \emph{Time-To-Close} of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance; even though 
we passed a filter for not fetching tickets still marked as Open, there was a small number erronously retrieved by Jira). 
In order to compute correct results, we run the same checks on issues as the ones listed in the analyse command (e.g. plot 
only tickets of high priority). Afterwards, we save either scatter plots or bar charts to disk presenting relationships 
between all the variables we tested.

@@

The data that we collected is stored, as previously mentioned, in a Bolt database instance which is around 6 GB in size. 
All tickets are stored as key-value pairs, where the key is the ticket's unique ID (e.g. KAFKA-100) and the value is the 
JSON encoded representation of the ticket. The tickets stored have the following fields available for investigation:
\begin{itemize}
  \item attachments - files or images attached to tickets;
  \item summary - short description of the ticket;
  \item description - more detailed information regarding what is requested or what bug was encountered;
  \item time estimate - estimated number of hours to complete the task (set by triagers or developers);
  \item time spent - time period between opening the ticket and a specific point in time;
  \item created timestamp;
  \item issue status - jira specific statuses, including Open, Closed, Awaiting Review, Patch Submitted;
  \item due date - optional deadline for when the ticket should get closed;
  \item comments - discussion around the ticket conducted by developers, end users, triagers;
  \item priority - it can range from low priority (minor) to critical/blocker;
  \item issue type - specific Jira field that specifies whether the ticket is either a bug, a feature request or a general task.
\end{itemize}

@@

In this section we present our results to the research questions we set to answer. We computed charts for all 
independent variables using either scatter plots for continuous variables (e.g. number of comments/\emph{Time-To-Close}) 
or bar charts for categorical variables (e.g. presence of attachments/\emph{Time-To-Close}). We also computed statistical analysis for 
all variables to test their significance and rank correlation coefficient and we will present each of them in their 
corresponding subsection.

@@

For every type of analysis, we also discuss possible reasons why certain correlations occured. Furthermore, for all 
of them we give possible solutions that could be implemented in order to maximise the ticket quality as cost-effective 
and efficient as possible.

@@

@@

Stack traces are active stack frames at a certain point in time while the program is executing. 
Many programming languages provide stack traces through their standard libraries, but the most 
popular proponents are Java and C\#. As Java is the main programming language used throughout 
the Apache Software Foundation projects (231 projects \cite{apache_projects}), many of the projects 
we collected (22) are also written in Java, thus we had a considerable chunk of data to analyze.

@@

@@

From the figure we cannot clearly deduce whether increased number of words in comments influence 
the Time-To-Close positively or negatively. Actually, we can assume at first sight that there is a descending trend implying more 
words produce smaller Time-To-Close values. However, the bulk of values plotted are in the range of 
1 to 1,600 total comment words per ticket (76,633 tickets) and in this slice of tickets, the trend is descending.
We did not generate the plot containing solely these values because there would still be 36,711 tickets left out. 
Therefore, the curve is skewed to the right, although the bulk of tickets that dictate the trend, are on the left side.

A correlational analysis run on all 201,786 tickets, however, releaved a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
This implies a statistically significant finding - as the number of comments increases, the \emph{Time-To-Close} value of the ticket 
also increases.

@@

The figure shows a very similar correlation to the one for comments complexity - graphically, it seems that as the number of words 
in summary and description increases, the Time-To-Close will decrease. This is true for the majority of the tickets 
which are in the range of 2 to 290 words, but as in the case of comments complexity analysis, we did not generate 
the plot only for those as we would have left 61,322 tickets out (out of a total of 201,786 tickets analysed).

@@

This is not a surprise - as previously mentioned, summary and description are the core components of any ticket. 
As summary is described by Jira, it should represent a short textual description of the bug or the feature request. However,
we have identified tickets having summaries with even more than 200 words. This is not optimal and might obfuscate
the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
Zimmermann et al. \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
reduce the effort invested by the developers.

Description, on the other hand, even though it is made to be a more detailed summary of the report, it should still be
within some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
with more than 4,000 words. Even though they included various types of information, including steps to reprodce, 
we believe that the reason why Jira and the other popular issue tracking systems created so many fields for bug reports 
is that the information that could all be put in description should be split across these fields: 
\begin{itemize}
  \item if there are stack traces or steps to reproduce, as we mentioned above, there should be specific fields 
  created exclusively for them; 
  \item if the end user is an experienced one and has reported numerous bugs or feature requests for the project, 
  they might also be able to provide an estimate for the difficulty of the task; however, that should be stored in the 
  Jira system field called Story Points;
  \item the user might also want to provide excerpts of code or previous discussions with other end users/developers; 
  however, they should not upload it inside the description field, but rather create a text attachment (e.g. markdown
  document) and attach it separately so that they keep the description clean and easy to follow.
\end{itemize}

@@

Another simple and straightforward solution can be the simple addition of hints below or above the text boxes for summary 
and description where administrators can write succint messages adivising reporters to not write verbose paragraphs 
unless they really have a very good reason to do so.

@@

However, we can not change this through automation like the solutions we presented in the previous 
analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
is inputting in the ticket as the costs would become unbearable very rapidly. Thus, what can be done to fix this? It is, 
after all, in the human nature to make mistakes, and mistyping is no exception. If we, for example, have some hint or a rule
in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters with a 
different language than English as their primary one would feel unwelcome and they might not get involved in the project anymore.

@@

A solution for pushing towards this ideal scenario would be expensive for the company, but the most efficient - have a 
sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
threshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
them against submitting the comment and encouraging them to be polite, engaging and friendly. One other solution
is a much more cost-effective one, but less efficient - the issue tracking system administrators could include a section 
in the code of conduct for the project stating that promoting a positive environment will help everyone. This way, people 
revolving around the project might be more inclined to be friendly.

@@

Furthermore, the project could greatly benefit from having access to closed source repositories in addition to the 
open source ones. Most closed source projects have much more structured planning, tracking and management activities - as 
Crowston et al. \cite{crowston2012free} present in their study, open source projects lack organized coordination which,
in the context of our study, means that people do not invest much effort into properly creating tickets in issue tracking 
systems, triaging efficiently, planning the work and tracking it. On the other hand, closed source projects follow 
more strict guidelines: standard working hours (would make tracking and linking the source code changes to tickets easier), 
adding story points (i.e. adding estimated difficulty or time to complete) and properly planning tickets before work 
starts on the task, tickets properly distributed to developers based on availability and expertise etc. These benefits 
of closed source projects would prove helpful for our analysis.

>>>>

In this research paper, we present and discuss our findings after running a quantitative data analysis 
on over 300,000 tickets taken from more than 38 open source projects. To this aim, we implemented a Go application 
with multiple commands (i.e. store, analyse, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyse them, generate plots and run statistical tests.

@@

Another research paper that strengthens the argument that readability is a quality 
factor in software tickets is the one presented by Hooimeijer et al. \cite{hooimeijer2007modeling}.
They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
investigating readability, daily load, submitter reputation, the whole changelog histories 
and severity. They conclude that not only readability in the textual fields of a ticket
influences the \emph{Time-To-Close}, but also that the presence of attachments and 
the number of comments have a clear lowering effect on the duration of triaging. On the 
other hand, the patch count and other similar fields did not provide significant 
value to the quality of tickets.

@@

The first information to be filled in by end users or developers on any issue tracking system
is the summary field, which holds a small description, usually between 5 and 30 words, of 
the request or bug being reported. In the study conducted by Rastkar et al. \cite{rastkar2010summarizing}, 
the authors investigated whether tickets could be summarised automatically and efficiently. What 
that implies is that developers would no longer be required to look at tickets on the whole, comprising of 
a large number of fields, but rather at a simple summary of a couple of lines 
encapsulating the whole information. The authors selected the Mozilla, Eclipse, GNOME and KDE 
open source projects and they asked volunteering university students to annotate 
the tickets in the issue tracking systems. More specifically, they wrote a summary 
of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
In parallel, Machine Learning algorithms were also employed to parse these summaries and 
learn how to efficiently create automated summaries for new bug reports. After both methods had been run, 
software developers were asked to rate these auto-generated summaries against the original ones; 
the conclusion was that existing conversation-based extractive summary generators used 
for software tickets produce the best results.

The work of Just et al. \cite{just2008towards} examines a rather different aspect
of quality in tickets - they are investigating the quality of the underlying issue 
tracking systems instead. 
After running a survey on 175 developers from Eclipse, Apache and Mozilla,
the authors applied a card sort in order to organise the comments into hierarchies to 
identify common patterns. Their findings can be summarised in the following top seven
suggestions: create differentiation between bug report difficulty levels between 
novices and experiences reporters, encourage users to input as much information as possible, 
add ability to merge tickets when needed, recognise and reward valuable bug reporters, integrate 
reputation into user profiles to mark experienced reporters and ensure the ability to expressively search through tickets.

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et al. \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps: extract and organise tickets, 
pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
The conclusions they drew from running the evaluation process were rather 
interesting: terms such as segfault, deadlock, crash, hand or memory typically indicate
a severe bug, when analyzing the textual description they found that using simple
one line summaries resulted in less false positives and increased precision
levels, the classifier needs a large number of tickets in order to predict correctly, 
depending on how well a software project is modularised and, lastly, one can 
use a predictor per module rather than a universal one.

@@

\section{Building the Data Set}\label{building}
The first step towards building the data set was to create a tool that was able to execute all the necessary commands:
fetching the tickets from any Jira instance, storing them into some form of database, analyse the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in mind, thus making it easy for others who might join the project to read 
    and understand the codebase; this would prove useful for developing the tool further;
    \item it is a compiled, statically typed language that produces cross-platform executables when building the application;
    this is helpful for our research as we can use any machine or cluster of computers regardless of the operating system 
    running on them and collect even larger number of tickets than what we have collected so far;
    \item it is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
    in our case, it helps by allowing access to goroutines, very lightweight threads that can scale even up to 
    millions; we use this powerful concept while fetching tickets from Jira or storing in the database - at one point, there were 
    more than 30,000 goroutines running at the same time.
  \end{itemize}

@@

This is the first command implemented in our tool - it is designed to fetch, from any valid Jira URL, any number of tickets 
and then store everything inside an instance of BoltDB \cite{bolt}, a key-value pair 
database. The whole process is parallelised with the possibility of scaling even up to hundreds of goroutines
(i.e. lightweight threads) running concurrently.

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyse command first 
fetches all the issues in the database. The next step is to filter out the tickets based on the following criteria:
\begin{itemize}
  \item tickets are \emph{High Priority} - the ticket status marked as either Blocker, Critical, Major or High;
  \item tickets are closed with a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
  higher bound as well in order to eliminate outliers retrieved by Jira);
  \item remove outliers for all categories - some fields had extreme values for a small number of tickets (e.g. one ticket
  had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
  produced correct results (they were removed as they were skewing the results due to erroneous completion of fields).
\end{itemize}

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlined in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence \emph{Time-To-Close} and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence \emph{Time-To-Close} the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the \emph{Time-To-Close} of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance; even though 
we passed a filter for not fetching tickets still marked as Open, there was a small number erroneously retrieved by Jira). 
In order to compute correct results, we run the same checks on issues as the ones listed in the analyse command (e.g. plot 
only tickets of high priority). Afterwards, we save either scatter plots or bar charts to disk presenting relationships 
between all the variables we tested.

@@

The data that we collected is stored, as previously mentioned, in a Bolt database instance which is around 6 GB in size. 
All tickets are stored as key-value pairs, where the key is the ticket's unique ID (e.g. KAFKA-100) and the value is the 
JSON encoded representation of the ticket. The tickets stored have the following fields available for investigation:
\begin{itemize}
  \item attachments - files or images attached to tickets;
  \item summary - short description of the ticket;
  \item description - more detailed information regarding what is requested or what bug was encountered;
  \item time estimate - estimated number of hours to complete the task (set by triagers or developers);
  \item time spent - time period between opening the ticket and a specific point in time;
  \item created timestamp;
  \item issue status - Jira specific statuses, including Open, Closed, Awaiting Review, Patch Submitted;
  \item due date - optional deadline for when the ticket should get closed;
  \item comments - discussion around the ticket conducted by developers, end users, triagers;
  \item priority - it can range from low priority (minor) to critical/blocker;
  \item issue type - specific Jira field that specifies whether the ticket is either a bug, a feature request or a general task.
\end{itemize}

@@

In this section we present our results to the research questions we set to answer. We computed charts for all 
independent variables using either scatter plots for continuous variables (e.g. number of comments / \emph{Time-To-Close}) 
or bar charts for categorical variables (e.g. presence of attachments / \emph{Time-To-Close}). We also computed statistical analysis for 
all variables to test their significance and rank correlation coefficient and we will present each of them in their 
corresponding subsection.

@@

For every type of analysis, we also discuss possible reasons why certain correlations occurred. Furthermore, for all 
of them we give possible solutions that could be implemented in order to maximise the ticket quality as cost-effective 
and efficient as possible.

@@

\vskip20pt

@@

Stack traces are active stack frames at a certain point in time while the program is executing. 
Many programming languages provide stack traces through their standard libraries, but the most 
popular proponents are Java and C\#. As Java is the main programming language used throughout 
the Apache Software Foundation projects (231 projects \cite{apache_projects}), many of the projects 
we collected (22) are also written in Java, thus we had a considerable chunk of data to analyse.

@@

\vskip35pt

@@

From the figure we cannot clearly deduce whether increased number of words in comments influence 
the Time-To-Close positively or negatively. Actually, we can assume at first sight that there is a descending trend implying more 
words produce smaller Time-To-Close values. However, the bulk of values plotted are in the range of 
1 to 1,600 total comment words per ticket (76,633 tickets) and for this majority of tickets, the trend is ascending.
We could not generate the plot based solely on these values as there would have been 36,711 tickets left out. 
Therefore, the curve is skewed to the right, although the bulk of tickets that dictate the trend, are on the left side.

A correlational analysis run on all 201,786 tickets, however, revealed a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
This implies a statistically significant finding - as the number of comments increases, the \emph{Time-To-Close} value of the ticket 
also increases.

@@

The figure shows a very similar correlation to the one for comments complexity - graphically, it seems that as the number of words 
in summary and description increases, the Time-To-Close will decrease. However, when numbers are run, the opposite trend 
surfaces. The majority of the tickets are in the range of 2 to 290 words, but as in the case of comments complexity analysis, 
we could not generate the plot only for those as we would have left 61,322 tickets out (out of a total of 201,786 tickets analysed). 
Therefore, the curve is skewed to the right, although the bulk of tickets that dictate the trend, are on the left side.

@@

This is not a surprise - as previously mentioned, summary and description are the core components of any ticket. 
As summary is described by Jira, it should represent a short textual description of the bug or the feature request. However,
we have identified tickets having summaries with even more than 200 words. This is not optimal and might obfuscate
the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
Zimmermann et al. \cite{zimmermann2010makes} present in their study is that a good, succinct summary can significantly 
reduce the effort invested by the developers.

Description, on the other hand, even though it is made to be a more detailed summary of the report, it should still be
within some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
with more than 4,000 words. Even though they included various types of information, including steps to reproduce, 
we believe that the reason why Jira and the other popular issue tracking systems created so many fields for bug reports 
is that the information that could all be put in description should be split across these fields: 
\begin{itemize}
  \item if there are stack traces or steps to reproduce, as we mentioned above, there should be specific fields 
  created exclusively for them; 
  \item if the end user is an experienced one and has reported numerous bugs or feature requests for the project, 
  they might also be able to provide an estimate for the difficulty of the task; however, that should be stored in the 
  Jira system field called Story Points;
  \item the user might also want to provide excerpts of code or previous discussions with other end users/developers; 
  however, they should not upload it inside the description field, but rather create a text attachment (e.g. markdown
  document) and attach it separately so that they keep the description clean and easy to follow.
\end{itemize}

@@

Another simple and straightforward solution can be the simple addition of hints below or above the text boxes for summary 
and description where administrators can write succinct messages advising reporters to not write verbose paragraphs 
unless they really have a very good reason to do so.

@@

However, we can not change this through automation like the solutions we presented in the previous 
analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
is inputting in the ticket as the costs would become unbearable very rapidly. Thus, what can be done to fix this? It is, 
after all, in the human nature to make mistakes, and mistyping is no exception. If we, for example, have some hint or a rule
in the code of conduct for the project stating that everything should be 100\% grammatically correct, many reporters with a 
different language than English as their primary one would feel unwelcome and they might not get involved in the project anymore.

@@

A solution for pushing towards this ideal scenario would be expensive for the company, but the most efficient - have a 
sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
threshold and it is believed that they are becoming rude or impolite, there could be a warning/pop-up on the screen advising 
them against submitting the comment and encouraging them to be polite, engaging and friendly. One other solution
is a much more cost-effective one, but less efficient - the issue tracking system administrators could include a section 
in the code of conduct for the project stating that promoting a positive environment will help everyone. This way, people 
revolving around the project might be more inclined to be friendly.

@@

Furthermore, the project could greatly benefit from having access to closed source repositories in addition to the 
open source ones. Most closed source projects have much more structured planning, tracking and management activities - as 
Crowston et al. \cite{crowston2012free} present in their study, open source projects lack organised coordination which,
in the context of our study, means that people do not invest much effort into properly creating tickets in issue tracking 
systems, triaging efficiently, planning the work and tracking it. On the other hand, closed source projects follow 
more strict guidelines: standard working hours (would make tracking and linking the source code changes to tickets easier), 
adding story points (i.e. adding estimated difficulty or time to complete) and properly planning tickets before work 
starts on the task, tickets properly distributed to developers based on availability and expertise etc. These benefits 
of closed source projects would prove helpful for our analysis.
